Time and space specifications for stencils

### 2016-05-17 paper.tex
new grammar proposal

\documentclass[10pt]{sigplanconf}

@@

\begin{figure}
\begin{align*}
\textit{specs} ::= & \; \textit{spec} \; \texttt{;} \; \textit{specs} \, \mid \, \textit{spec} \\
%
\textit{spec} :: = & \; \texttt{v} : S \\[0.5em]
S ::= &  \; \texttt{forward} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{backward} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{centered} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{unspecified} \; [\texttt{dims=}\textit{dims}] \\
& \; \mid \texttt{read-once} \; S \\[0.5em]
\textit{depth} ::= & \; \mathbb{N} \, \mid \, \textit{temp-spec} \\ 
\textit{temp-spec} ::= & \; \mathbb{N}\{var\} \\
\textit{dims} ::= & \; \mathbb{D} \; \texttt{,} \; \textit{dims} \, \mid
                    \, \mathbb{D} \\
\mathbb{D}  ::= & \; \mathbb{N}_{>0} \, \mid \, \texttt{t}
\end{align*}
\caption{Syntax of specifications}
\label{fig:syntax}
\end{figure}

>>>>

\documentclass[9pt]{sigplanconf}

@@

\begin{figure}
\dnote{NEW grammar}
\begin{align*}
S_\odot ::= \; & \texttt{forward} \; [,\texttt{depth=}\mathbb{N}] \; 
        , \texttt{dims}=\textit{dims}_\odot  \\
\mid \; & \texttt{backward} \; [,\texttt{depth=}\mathbb{N}] \; , \texttt{dims=}\textit{dims}_\odot \\
\mid \; & \texttt{centered} \; [,\texttt{depth=}\mathbb{N}] \; , \texttt{dims=}\textit{dims}_\odot \\ \\
\textit{prodS} ::= \; & S_{\texttt{*}}  \; \texttt{*} \; Sprod \mid \epsilon \\
\textit{sumS} ::= \; & \textit{prodS} \; \texttt{+} \; \textit{sumS} \mid S_{\texttt{+}} \; \texttt{+}
          \; \textit{sumS} \mid \epsilon \\ 
\textit{modS} ::= \; & 
  [\texttt{read-once}] \\
  & [, \texttt{reflexive} \; \texttt{dims=}\textit{dims}{\texttt{,}}] \\
  & [, \texttt{irreflexive} \;
    \texttt{dims=}\textit{dims}{\texttt{,}}] \; \textit{sumS} \\ 
\textit{temporal} ::= \; & \ldots \\ 
\textit{spec} ::= \; & \texttt{v :} \; [\textit{modS}] \; [\textit{temporal}]   \\ \\
\textit{dims}_\odot ::= & \; \mathbb{D} \; \odot \; \textit{dims}_{\odot} \mid \mathbb{D}
%
%dims = dims+ | dims*
%dims+ = D + dims+ | dims+
%dims* = D * dims* | dims*%
%
%Smod = Linear Spa | NonLinear Spa
\end{align*}

\dnote{OLD grammar}
\begin{align*}
\textit{specs} ::= & \; \textit{spec} \; \texttt{;} \; \textit{specs} \, \mid \, \textit{spec} \\
%
\textit{spec} :: = & \; \texttt{v} : S \\[0.5em]
S ::= &  \; \texttt{forward}, \; [\texttt{depth=}\textit{depth}], \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{backward}, \; [\texttt{depth=}\textit{depth}], \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{centered}, \; [\texttt{depth=}\textit{depth}], \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{unspecified}, \; [\texttt{dims=}\textit{dims}] \\
& \; \mid \texttt{reflexive}\, \; 
& \; \mid \texttt{irreflexive}, \; \textit{spec}
& \; \mid \textit{spec} \; \texttt{\&} \; \textit{spec} \\
& \; \mid \texttt{read-once} \; S \\[0.5em]
\textit{depth} ::= & \; \mathbb{N} \, \mid \, \textit{temp-spec} \\ 
\textit{temp-spec} ::= & \; \mathbb{N}\{var\} \\
\textit{dims} ::= & \; \mathbb{D} \; \texttt{,} \; \textit{dims} \, \mid
                    \, \mathbb{D} \\
\mathbb{D}  ::= & \; \mathbb{N}_{>0} \, \mid \, \texttt{t}
\end{align*}
\caption{Specification syntax}
\label{fig:syntax}
\end{figure}
